\bf Eye Fitting Straight Lines in the Modern Era

### 2022-01-24 Eye-Fitting-Straight-Lines-in-the-Modern-Era.Rmd
working on edits.

keywords:
- Graphics
- Regression
- Graph Perception
- Scatterplot
- Cognitive Bias

@@

```{r load-packages, include = F}
library(readr)
library(tidyverse)
library(knitr)
library(gridExtra)
library(patchwork)
library(cowplot)
library(ggforce)
```

@@

eyefitting_example_sim <- read.csv("data/youdrawit-eyefitting-simdata-example.csv")

>>>>

keywords:
- Cognitive Bias
- Graph Perception
- Graphical Testing
- Linear Regression
- Statistical Graphics

@@

```{r load-packages, include = F}
library(readr)
library(tidyverse)
library(knitr)
library(gridExtra)
library(patchwork)
library(cowplot)
library(ggforce)
library(here)
```

@@

eyefitting_example_sim <- read.csv(here("data/youdrawit-eyefitting-simdata-example.csv"))

### 2022-01-24 Eye-Fitting-Straight-Lines-in-the-Modern-Era.tex
working on edits.

\noindent%
{\it Keywords:} Graphics, Regression, Graph
Perception, Scatterplot, Cognitive Bias
\vfill

@@

--\textgreater{}

@@

\item[Title:] Brief description. (file type)

\item[R-package for  MYNEW routine:] R-package <U+FFFD>MYNEW<U+FFFD> containing code to perform the diagnostic methods described in the article. The package also contains all datasets used as examples in the article. (GNU zipped tar file)

\item[HIV data set:] Data set used in the illustration of MYNEW method in Section~ 3.2. (.txt file)

>>>>

\noindent%
{\it Keywords:} Cognitive Bias, Graph Perception, Graphical
Testing, Linear Regression, Statistical Graphics
\vfill

@@

@@

\item[Participant Data:] De-identified participant data can be found at ...

\item[Data Analysis Code:]
